Tables/Graphs for Article

### 2018-01-26 article/draft1.Rnw
resolved issue with text

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = \Sexpr{round(unname(model$stat[8]), 2)}$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums have become widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to save money and reduce electronic waste. This company provides over 30,000 free online repair guides and sells specialized tools and parts needed for such repairs.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and developed a taxonomy for classifying such questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{2cm} | L{10cm} |}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name dDevice name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and continuous variables derived}
\label{table:variables}
\end{table}

@@

All computation was executed under \texttt{R} version 3.4.3.  Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R. To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package. This function uses the Cox model and a vector of times to compute predicted survival probabilities. Data used for this analysis can be found in the \texttt{oshitar} package. The function \texttt{variable\_setup} of the \texttt{oshitar} package was used to set up all necessary variables in the data.

@@

  Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was \Sexpr{mean} hours, or \Sexpr{round(mean / 24, 2)} days. The median survival time, the time at which 50\% of the questions in the data received an answer, was \Sexpr{median} hours.

@@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions; each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations resulted in univariate p-values of less than 0.001. For variables that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics of final model (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device name (e.g. a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name at all. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways that the CQA can be structured to potentially decrease response times. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include additional tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
\hline
\textbf{Device} & iPhone 6 & android tablet \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & touch screen not worki\\ \hline
\textbf{Tags} & touchscreen, water damage & NA\\ \hline
\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
\textbf{Device Category} & Apple Product & Tablet \\ \hline
\textbf{Day Posted} & Weekday & Weekday \\ \hline
\textbf{Text length (characters)} & 241 & 81 \\ \hline
\textbf{Device name length (characters)} & 8 & 18\\ \hline
\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
\textbf{Text contain end punctuation?} & True & False \\ \hline
\textbf{Text in all lower case?} & False & True \\ \hline
\textbf{Title end in a question mark?} & False & False \\ \hline
\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
\textbf{User indicate prior effort?} & False & False \\ \hline
\textbf{User update question after posting?} & False & False \\ \hline
\textbf{Frequently-used answered words?} & True & True \\ \hline
\textbf{Frequently-used unanswered words?} & False & False \\ \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}
Table \ref{table:questions} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet). All fields in device, title, text, and tags are shown as the users entered it.

@@

To create the variables, the data was separated between answered and unanswered questions. For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency. The same was performed for the data frame containing unanswered questions. ``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions. To determine the latter, a ratio of frequencies was assessed. The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20). Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions. As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists. Table \ref{table:frequentterms} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words). 
% Table with list of frequently-used words
\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|L{8cm}|}
  \hline
 \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, LCD, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\label{table:frequentterms}
\end{table}

>>>>

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

Community-driven online question and answer forums have become widely-used sources of information. These online platforms feature thousands of user-posted questions and answers and receive millions of visits every month. The CQA analyzed in this paper is iFixit's \textit{Answers} forum. Founded in 2003, iFixit provides over 30,000 free online repair guides and sells the specialized tools and parts needed for such repairs. This company's mission is to equip users with the knowledge and tools necessary to repair their broken devices, as part of an effort to help them save money and reduce electronic waste.

@@

With the recent increase in the popularity and use of CQAs, these data-rich platforms have been the subject of a multitude of studies. Regarding analysis of response times, \cite{Bhat2014} developed a classification model using both textual and non-textual features to estimate response times for questions posted on \textit{Stack Overflow}. \cite{Mahmud2013} used parametric methods and proposed models to predict response times based on exponential distributions. \cite{Asaduzzaman2013} instead focused exclusively on unanswered questions and created a model to predict how long a question would remain unanswered. However, all research mentioned restricted analysis to either questions for which response times were observed or to questions that remained unanswered. The research presented in this paper uses survival analysis, a method not yet applied to CQAs, to allow for analysis of both answered and unanswered questions in a unified framework.

@@

% Table of derived predictors
\begin{table}[!htbp]
\centering
\begin{tabular}{| L{2cm} | L{10cm} |}
  \hline
  \multirow{9}{2cm}{\textbf{Categorical Variables}} & Device category the question pertains to. Categories include: Android/Other Phone, Apple Products, Camera, Electronics, Game Console, Home, Other, PC, Tablet, Vehicle \\ \cline{2-2}
  & If the question was posted on a weekend or on a weekday \\ \cline{2-2}
  & If the question's text contains end punctuation marks (. ? !) \\ \cline{2-2}
  & If the question's text is in all lower case \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among answered questions \\ \cline{2-2}
  & If the question's title contains at least one word considered to be ``frequently-used'' among unanswered question \\ \cline{2-2}
  & If the question's title ends in a question mark \\ \cline{2-2}
  & If the user edited or added information to the question's text after posting it \\ \cline{2-2}
  & If the user made an effort to solve the problem prior to asking the question \\ \hline
  \multirow{5}{2cm}{\textbf{Continuous Variables}} & Average number of characters in each question's tags (average tag length)\\ \cline{2-2}
  & Average frequency for all of a question's tags (average tag frequency) \\ \cline{2-2}
  & Number of characters in the question's text (text length) \\ \cline{2-2}
  & Number of characters in the user-defined device name (device name length) \\ \cline{2-2}
  & Ratio of the number of line breaks to the number of characters in the question's text (line break to text length ratio) \\ \hline
\end{tabular}
\caption{Categorical and continuous variables derived}
\label{table:variables}
\end{table}

@@

All computation was executed under \texttt{R} version 3.4.3.  Kaplan-Meier estimates of survival probability were computed with the \texttt{Surv} and \texttt{survfit} functions of the \texttt{Survival} package in R. To compute predicted survival probabilities using the final model, the \texttt{predictSurvProb} function was used from the \texttt{pec} package. This function uses the Cox model and a vector of times to compute predictions. Data used for this analysis can be found in the \texttt{oshitar} package. The function \texttt{variable\_setup} of the \texttt{oshitar} package was used to set up all necessary variables in the data.

@@

Figure \ref{fig:kmcurve} shows the Kaplan-Meier estimated survival probability curve for all questions in the data. The curve indicates that if a question does not receive an answer within the first 100 hours after it has been posted, the likelihood of it receiving an answer in the future is low. The Kaplan-Meier estimated mean survival time, or the average time until a question received its first answer was 775.75 hours, or 32.32 days. The median survival time, the time at which 50\% of the questions in the data received an answer, was 9.16 hours.

@@

Each training set contained \Sexpr{format(nrow(train1), big.mark = ",")} questions; each test set contained \Sexpr{format(nrow(test1), big.mark = ",")} questions. Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations to all continuous predictors resulted in univariate p-values of less than 0.001. For variables that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

@@

% Cross-validation metrics
\begin{table}[!htbp]
\centering
\begin{tabular}{| r | r | r | r | r  | r | r | r |}
  \hline
 & \textbf{HR} & \textbf{LR} & \textbf{p-value} & \textbf{$R^2$} & \textbf{\textit{Dxy}} & \textbf{Concordance} \\ 
  \hline
  \textbf{Training Sets} & 2.03 & 937.39  & <0.0001 & 0.14 & 0.27 & 0.63 \\ 
  \textbf{Test Sets}     & 1.99 & 220.83  & <0.0001 & 0.14 & 0.26 & 0.63 \\
  \textbf{Full Data}     & 2.03 & 1165.03 & <0.0001 & 0.14 & 0.28 & 0.63 \\ 
   \hline
\end{tabular}
\caption{Performance metrics of final model. (HR: Hazard Ratio, LR: Partial Likelihood Ratio)} 
\label{table:cv}
\end{table}

@@

The model's weak predictive accuracy, which may be explained by limitations in the data, lead to suggestions for changes in CQA design. Many users incorrectly specified the device name (e.g. a user asking a question about a Turtle Beach Ear Force XO ONE headset defined the device name as, ``Turtle Beach Ear Force Xmy grandson chewed through the wire while he was playing it's brand-new is there anyway I can have it fixed0 One''), or did not include a device name. Many users also incorrectly used the tagging system by including ambiguous and lengthy tags like ``someone sat on it :('' or ``help me please!!!!!'' (tags are generally a couple key words that allow the answering community to quickly discern the question's topic). It is likely that these inconsistencies contributed to the final model's low predictive power. This, along with the results of the final model, reveal some of the ways the CQA can be structured to potentially decrease response times. As findings indicate that questions with correctly defined tags and device names may lead to quicker response times, the CQA can provide a stricter framework for asking questions. Allowing users to enter any device name or tag leaves room for user error, shown by the examples described above. Instead, the CQA can restrict the tags or devices that users can include to a drop-down list. The CQA can also include more tips to guide users asking questions. Implementing a more structured framework for asking questions can help users create understandable and clear questions and in turn decrease response time, as well as create a set of consistent questions for improved analysis.

@@

\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|L{5cm}|L{5cm}|}
\hline
\textbf{Device} & iPhone 6 & android tablet \\ \hline
\textbf{Title} & iPhone water damage, touch screen issue & ccccaaaan you help me fix my touch screen \\ \hline
\textbf{Text} & So I dropped my iPhone in water 4 days ago. Have done the whole rice thing and seen huge difference in it. However, only one side of my screen works and it is the one side which I need to unlock the phone. What would be the best way forward? & touch screen not worki\\ \hline
\textbf{Tags} & touchscreen, water damage & NA\\ \hline
\textbf{Response Time (hrs)} & 1.361 & NA \\ \hline 
\textbf{Device Category} & Apple Product & Tablet \\ \hline
\textbf{Day Posted} & Weekday & Weekday \\ \hline
\textbf{Text length (characters)} & 241 & 81 \\ \hline
\textbf{Device name length (characters)} & 8 & 18\\ \hline
\textbf{Average tag length (characters)} & 11.5 & 47 \\ \hline
\textbf{Average tag frequency} & 0.0097 & 0 \\ \hline
\textbf{Text contain end punctuation?} & True & False \\ \hline
\textbf{Text in all lower case?} & False & True \\ \hline
\textbf{Title end in a question mark?} & False & False \\ \hline
\textbf{Line break to text length ratio} & 0 & 0 \\ \hline
\textbf{User indicate prior effort?} & False & False \\ \hline
\textbf{User update question after posting?} & False & False \\ \hline
\textbf{Frequently-used answered words?} & True & True \\ \hline
\textbf{Frequently-used unanswered words?} & False & False \\ \hline
\end{tabular}
\caption{Answered and unanswered questions}
\label{table:questions}
\end{table}

Table \ref{table:questions} provides observed and derived variable values from an example of an answered question (regarding the iPhone 6) and unanswered question (regarding android tablet). All fields in device, title, text, and tags are shown as the users entered it.

@@

To create the variables, the data was separated between answered and unanswered questions. For the data frame containing answered questions, text mining techniques were used to create a list of every word within each questions' titles and the proportion of times those words occurred among all answered questions' titles, defined as the frequency. The same was performed for the data frame containing unanswered questions. ``Frequently-used'' words in answered questions were defined as those that appeared in 1\% or more of all answered questions' titles, and appeared in more answered questions than in unanswered questions. To determine the latter, a ratio of frequencies was assessed. The ratio was calculated as the proportion of times a word occurred among answered questions, to the proportion of times a word occurred in unanswered questions. As an example, if ``cracked'' appeared in 2\% of answered questions and 0.1\% of unanswered questions, it would be considered ``frequently-used'' among answered questions as it occurs in more than 1\% of answered questions' titles and occurs 20 times more in answered question than in unanswered questions (ratio = 0.02/0.001 = 20). Similarly, ``frequently-used'' words in unanswered questions must occur in 1\% or more of all unanswered question's titles and occur in more unanswered questions than answered questions. As there was some overlap between ``frequently-used'' words in each list and levels of the device categorization variable, every word that matched a device name was removed from the lists. Table \ref{table:frequentterms} contains the resulting terms for answered questions (111 words) and for unanswered questions (32 words).

% Table with list of frequently-used words
\begin{table}[!htbp]
\centering
\begin{tabular}{|L{4cm}|L{8cm}|}
  \hline
 \textbf{Frequently-used terms among answered questions} & screen, turn, working, replacement, power, work, replace, charging, charge, button, touch, black, turning, broken, start, stuck, new, LCD, upgrade, problem, change, port, replaced, card, open, boot, replacing, remove, reset, back, drive, error, cable, ssd, cracked, hard, one, dropped, logic, lines, white, keeps, pro, dead, now, front, damage, switch, parts, glass, still, charger, issue, sim, turns, digitizer, just, mode, model, backlight, usb, stopped, logo, starting, know, unresponsive, password, factory, call, use, damaged, find, sensor, possible, fixed, side, galaxy, data, ipod, problems, issue, slow, system, connector, without, overheating, code, ram, air, microphone, please, red, much, plugged, getting, booting, left, way, buy, plus, time, loose, lock, coming, got, shuts, says, install, key, door, top \\
  \hline
  \textbf{Frequently-used terms among unanswered questions} & sound, light, wifi, speaker, connect, picture, stay, noise, bluetooth, isnt, apps, going, rear, question, play, stop, service, take, hear, lights, showing, network, volume, come, keep, connection, flashing, shut, print, blue, buttons, edit \\ 
   \hline
\end{tabular}
\caption{Frequently-used terms among answered and unanswered questions' titles, ordered by decreasing frequency}
\label{table:frequentterms}
\end{table}

### 2018-01-26 article/draft1.tex
resolved issue with text

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

Each training set contained 6,208 questions; each test set contained 1,552 questions. Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations resulted in univariate p-values of less than 0.001. For variables that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.

>>>>

Community-driven online question and answer forums (CQA), platforms that allow users to ask and answer questions, contain an extensive amount of crowd-sourced information. One such example of a CQA is iFixit's \textit{Answers} forum. This forum features user-asked questions related specifically to device repair, which are answered by both repair experts and everyday users. An important aspect of these CQAs, for both users and the forum, is question response time. This paper presents a survival analysis of the time until a question posted on iFixit's \textit{Answers} forum receives it's first response. A Cox proportional hazards model was developed to identify variables associated with response time. Though several predictors were significant, the model's predictive accuracy was low ($R^2 = 0.15$). Significant predictors included the device category of the question (questions pertaining to Apple products received answers faster than others (HR = 2.54, 95\% CI = (2.32, 2.79)), factors related to the question's title (e.g., if it was phrased as a question (HR = 1.29, 95\% CI = (1.21, 1.38))), and the day of the week the question was posted (questions posted over the weekend received answers slower than those posted on a weekday (HR = 0.87, 95\% CI = (0.82, 0.93))). Future studies can investigate whether factors identified as significant in this analysis can be generalized to other CQAs.

@@

Each training set contained 6,208 questions; each test set contained 1,552 questions. Univariate analysis performed on one training set indicated that all categorical predictors were significant with partial likelihood ratio p-values of less than 0.001. Continuous predictors, excluding device length and average tag length, also resulted in univariate p-values of less than 0.001. Applying either square root or log transformations to all continuous predictors resulted in univariate p-values of less than 0.001. For variables that contained zeros, one was added to each observation before applying the log transformation. The following transformations were applied to continuous variables: square root transformation of average tag frequency, log plus one transformation of average tag length, log plus one transformation of device name length, square root transformation of line break to text length ratio, and log transformation of text length. All categorical predictors and all continuous predictors with necessary transformations were retained for the full model.
